Palomar 5 Gaps

### 2024-10-22 paper/main.tex
started paragraph for carlberg gap creation rate quantity

    \textbf{\textit{Action item:}} I need to make sure I check out real good the papers that investigate the gaps from Palomar 5. I wanna compare this to the known length of Palomar 5, how does this reduce the results, and are there observed gaps in Palomar 5 that are consistent with these simulations?

>>>>

      Lastly, \citet{2012ApJ...748...20C} conceptualized the number of gaps with a statistical quantity, the rate at which gaps are created per unit stream-length. To put our results in these terms, the global cluster population has a gap creation rate on Palomar 5 of XXX.
